---
title: "Assignment-SQL and R"
author: "Mahmud Hasan Al Raji"
date: "`r Sys.Date()`"
output: html_document
---
## R chunk Setup:
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Required Packages and libraries:
```{r packages and library}
install.packages("RMySQL")
installed.packages("RODBC")
install.packages("DBI")
library(RMySQL)
library(RODBC)
library(DBI)
library(dplyr)
library(tidyverse)
```
## Connecting MysQL databasse with R:
```{r}
db=dbConnect(RMySQL::MySQL(),
   dbname='mydatabase',
   port= 3306,
   host='localhost',
   user='root',
   password=rstudioapi::askForPassword("database password"))
```
##Table names:

```{r}
dbListTables(db)
```
## Running SQL query to get movie_view table:

```{r}
movie_view <- dbGetQuery(db,"SELECT * FROM `movie viewer status`;")
movie_view
```

##Running SQL query to get 'movie_rating' table

```{r }
movie_rating <- dbGetQuery(db,"SELECT * FROM `movie rating`;")
movie_rating
```

#Running SQL query to join table

```{r join_table}
join_table<-dbGetQuery(db,"SELECT* FROM 
                      `movie viewer status` mv
                      JOIN `movie rating` mr
                       ON mv.`movie name`=mr.`movie name`;")
join_table             
```

##Subsetting dataframe

```{r}
df1 <- subset(movie_rating, select=c("monir rate", "karim rate", "joseph rate", "prakash rate", "arony rate")) 
df1
```
##Row values summation with handling missing values to get total point table:

```{r}
total_point<-rowSums(df1, na.rm=TRUE)
total_point
```

#Addition of new column to movie_rating table:
```{r}
df2<-cbind(movie_rating,total_point)
df2
```
## Subsetting to get final table showing movie wise total point:
```{r}
df_final <- subset(df2,select=c("movie name","total_point"))
df_final
```

## Conclusion: From the data analysis above, it is found that"the territory" is the most popular movie in this survey.  



